
\bibitem{2part-1}
	За пределами Стандартной модели
	[Электронный ресурс].
	— Режим доступа: https://elementy.ru/LHC/HEP/SM/beyondSM 
	— Да­та доступа: 11.12.2017.

\bibitem{2part-pythia-all}
	Official documentation
	[Электронный ресурс].
	— Режим доступа: http://home.thep.lu.se/~torbjorn/Pythia.html 
	— Дата доступа: 11.12.2017.

\bibitem{review-pythia}
	Леонтьев, В. В. 
	Информационные методы в физике высоких энергий 
	/ В. В. Леонтьев, И. И. Белотелов 
	— Москва : «Университетская книга», 2011.
% http://lib.sinp.msu.ru/static/tutorials/141_Leontiev_Zadahi_2011.pdf

\bibitem{review-powheg}
	Alioli, S. NLO and parton showers: the POWHEG-BOX
	/ Simone Alioli 
	// DESY, Platanenallee 6, 15738 Zeuthen, Germany – 2013. – Vol. 40. – P. 12.
% https://indico.desy.de/indico/event/1964/session/16/contribution/238/material/0/0.pdf

\bibitem{review-sherpa}
	Event generation with SHERPA
	/ Gleisberg, T. [et al.]  
	// Phys. Rev. D. – 2014. – Vol. 60. – P. 3.
% https://arxiv.org/format/0811.4622

\bibitem{2part-pankov}
	Osland, P. Probing $Z-Z^\prime$ mixing with ATLAS and CMS resonant diboson production data at the LHC at $\sqrt{s}=13$ TeV
	/ P. Osland, A.A. Pankov, A.V. Tsytrinov 
	// Physical Review D. – 2017. – Vol. 96. – P. 055040.
	
\bibitem{sirunyan:2017}
	Search for massive resonances decaying into $WW$, $WZ$ or $ZZ$ bosons in proton-proton collisions at $\sqrt{s}=13$ TeV
	/ Sirunyan, A. M. [et al.] 
	// J. High Energy Phys. – 2017. – Vol. 162. – P. 56.
	
\bibitem{main-book}
	Красников, Н.В. Новая физика на Большом адронном коллайдере / Н.В. Красников, В.А. Матвеев  
	// М.: КРАСАНД, 2011. – 208 с.
	
\bibitem{Krasnikov:2004}
	Н. В. Красников, В. А. 
	Матвеев. Поиск новой физики на LHC
	[Электронный ресурс].
	— Режим доступа: http://nuclphys.sinp.msu.ru/ATLAS\_exp/at03.htm 
	— Дата доступа: 11.12.2017.
	
\bibitem{nuclphys:weak}
	Слабое взаимодействие 
	[Электронный ресурс].
	— Режим доступа: http://nuclphys.sinp.msu.ru/enc/e149.htm
	— Дата доступа: 11.12.2017.
	
\bibitem{main-book2}
	Емельянов, В.М. Стандартная модель и ее расширения 
	// M.: ФИЗМАТЛИТ. -- 2007 – №584 – C. 55
	
\bibitem{Bobovnikov:2016}
	Бобовников, И.Д. Эффекты $Z-Z^\prime$-смешивания в процессах рождения пары $W^±$-бозонов на адронных и лептонных коллайдерах высоких энергий
	/ И.Д. Бобовников, А.А. Панков.
	— Письма в ЭЧАЯ, 2016. T. 13, №1(199). С.8-35
	
\bibitem{schael:2006}
	Patrignani, C. Review of Particle Physics 
	/ C. Patrignani et al. [Particle Data Group]
	// Chin. Phys. C. – 2016. – Vol. 40, No.10. – P. 100001.
	

\bibitem{andreev-pankov:2012}
	Andreev, V. V. Constraints on the $Z-Z^\prime$ mmixing angle from data measured for the process $e^+e^- \rightarrow W^+W^-$ at the LEP2 collider
	/ V.V. Andreev, A.A. Pankov
	// Phys. At. Nucl. – 2012. – Vol. 75. – P. 76.

\bibitem{ada-wwz:2013}
	Measurement of $W^+W^-$−production in pp collisions at $\sqrt{s}=7$ TeV with the ATLAS detector and limits on anomalous $WWZ$ and $WW_y$ couplings
	/ Ada, G. [et al.] 
	// Phys. Rev. D. – 2013. – Vol. 88. – P. 29.
	
\bibitem{ada-lvlv:2013}
	Search for new phenomena in the $WW \rightarrow lvl^{\prime}v^{\prime}$ final state in $pp$ collisions at $\sqrt{s}=7$ TeV with the ATLAS detector
	/ Ada, G. [et al.] 
	// Physics Letters B. – 2013. – Vol. 3. – P. 878.

% ---
% Статья



% Java book
\bibitem{java}
	Java: the complete reference. 
	/ Schildt H. 
	// McGraw-Hill Education Group, 2016. – P. 820.
% Spring book
\bibitem{spring}
	Aspectj in action: enterprise AOP with spring applications
	/ Laddad R. 
	// Manning Publications Co., 2014. – P. 254.
% Docker book
\bibitem{docker}
	Docker in action
	/ Nickoloff J.
	// Manning Publications Co., 2016. – P. 304.
% AWS Book https://aws.amazon.com/ru/what-is-aws/#most-functionality
\bibitem{aws}
	Amazon web services in action
	/ Wittig A.
	// Manning Publications Co., 2015. – P. 500.


	 
\bibitem{user-interface}
	 Designing the User Interface: Strategies for Effective Human-Computer
	 Interaction
	 / B. Shneiderman [et al]. – Pearson Education Limited, 2017. – 624 p. 

	 

	

% Book
	 

	




